Estimating the dynamics of SPARQL query results using binary classification

### 2019-08-05 main.tex
camera-ready updates following this comments: - In the introduction it is written: “(aiming for stronger consistency at the cost of more frequent updates),”, I would say “aiming for stronger consistency at the cost of more frequent querying”
- In Figure 8, for F1, Precision and Recall several red lines to
indicate results not using features from R. Why we have several lines?
Do they refer to different classification methods? Please clarify this.

- I regret that the experimentations are not reproducible. Code, data,
queries are not available. I believe the gold standard databases (RDF
data, qu

Since datasets change over time, long-running applications that cache and repeatedly use query results obtained from an external SPARQL endpoint may resubmit the queries regularly to ensure up-to-dateness. As a result, without further information as to the dynamics of a particular SPARQL query, applications face the choice of either performing frequent query executions that may be redundant and repeatedly return the same results (aiming for stronger consistency at the cost of more frequent updates), or performing infrequent query executions that may lead to stale data being persisted in the application when the underlying sources change (accepting weaker consistency to improve efficiency/scalability). Given the costs for clients and servers of repetitive requests served over the Web  and the potential efficiency gains offered by local caches, several weak consistency approaches have been proposed that try to keep the local data of the applications updated at lower cost by predicting changes~\cite{KnuthHS16,DividinoGS15,NishiokaS17}.

@@

	\end{axis}
	\end{tikzpicture}
	\caption{Best results for combination of features in term of $F_1$-measure (left), Precision score (center) and Recall (right) with increasing windows sizes; blue indicates results using features from \textsc{r} while red indicates results not using features from \textsc{r}
		\label{fig:result}}
\end{figure}

@@

We thus explore this trade-off experimentally. For this, we define some desirable characteristics for the queries and data used in the experimental setting, such as availability, size, dynamics, diversity, etc. Settling on Wikidata, we collect 23 versions and curate 221 user-generated queries from which we compute results, statistics and ultimately features that form the gold standard for the tasks. Analysing these data and queries, we conclude that they meet the desired characteristics, offering a large-scale, diverse, real-world setting; more importantly, we find that our queries offer an ideal distribution of queries whose results always change, queries whose results never change, and (more importantly) queries whose results change intermittently and for which prediction is thus non-trivial.

>>>>

Since datasets change over time, long-running applications that cache and repeatedly use query results obtained from an external SPARQL endpoint may resubmit the queries regularly to ensure up-to-dateness. As a result, without further information as to the dynamics of a particular SPARQL query, applications face the choice of either performing frequent query executions that may be redundant and repeatedly return the same results (aiming for stronger consistency at the cost of more frequent querying), or performing infrequent query executions that may lead to stale data being persisted in the application when the underlying sources change (accepting weaker consistency to improve efficiency/scalability). Given the costs for clients and servers of repetitive requests served over the Web  and the potential efficiency gains offered by local caches, several weak consistency approaches have been proposed that try to keep the local data of the applications updated at lower cost by predicting changes~\cite{KnuthHS16,DividinoGS15,NishiokaS17}.

@@

	\end{axis}
	\end{tikzpicture}
	\caption{Best results for combination of features in term of $F_1$-measure (left), Precision score (center) and Recall (right) with increasing windows sizes; blue indicates results using features from \textsc{r} (\textsc{r}, \textsc{qr}, \textsc{pr} and \textsc{qpr}) while red indicates results not using features from \textsc{r} (\textsc{q}, \textsc{p}, \textsc{qp} and the Baselines)
		\label{fig:result}}
\end{figure}

@@

We thus explore this trade-off experimentally. For this, we define some desirable characteristics for the queries and data used in the experimental setting, such as availability, size, dynamics, diversity, etc. Settling on Wikidata, we collect 23 versions and curate 221 user-generated queries from which we compute results, statistics and ultimately features that form the gold standard for the tasks. Analysing these data and queries, we conclude that they meet the desired characteristics, offering a large-scale, diverse, real-world setting; more importantly, we find that our queries offer an ideal distribution of queries whose results always change, queries whose results never change, and (more importantly) queries whose results change intermittently and for which prediction is thus non-trivial. We make this gold standard available at \url{https://users.dcc.uchile.cl/~amoya/quweda2019/}.
